Suplementary Material 4: Draw Interbirth Interval Predictons on the Last Birth Omited Data

### 2023-04-18 S4_draw_IBI_predictions_EE_not_last.Rmd
added residuals plot

  load(paste0(fitDir, "fits_PISH_obs.rda")) # load all fits all ~ 8 GB

@@

ggplot2::ggsave(file = "./exports/figS2.pdf", width = 188, height = 110, units = "mm")
ggplot2::ggsave(file = "./exports/figS2.png", width = 188, height = 110, units = "mm")
```

>>>>

  #load(paste0(fitDir, "fits_PISH_obs.rda")) # load all fits all ~ 8 GB

@@

ggsave(file = "./exports/figS2.pdf", width = 188, height = 110, units = "mm")
```
